alternativeRSA

### 2016-01-20 models/RSA_alternativeCostFormulation.Rmd
re-outputted full model runs data with modified saliency costs.

costs <- salienceCosts2
priors <- unifPriors
data <- left_join(speakerL08, costs) %>%
  left_join(., priors) %>%
  rowwise %>%
  select(scale, degree, stars, speaker.p, prior.p, cost) %>%
  group_by(scale)

@@

# write.csv(modelRunData, "model_data/allModelRuns.csv")
```

>>>>

costs <- salienceCosts5
priors <- unifPriors
data <- left_join(speakerL12, costs) %>%
  left_join(., priors) %>%
  rowwise %>%
  select(scale, degree, stars, speaker.p, prior.p, cost) %>%
  group_by(scale)

@@

# write.csv(modelRunData, "~/Desktop/Projects/scalar_implicature/models/model_data/allModelRuns.csv")
```
